Characterizing Signal Loss, Error, and Bias in the 21cm Reionization \\Power Spectrum: A Revised Study of PAPER-64

### 2018-01-11 PAPER.tex
finished josh edits

\begin{figure*}
	\centering
	\includegraphics[width=1\textwidth]{plots/sigloss_modeloop.png}
	\caption{Power spectra $2\sigma$ upper limits for $k=0.393$ h Mpc$^{-1}$ for fringe-rate filtered PAPER-64 data. Values 
are shown before (gray) and after (black) signal loss estimation as a function of number of eigenmodes of $\widehat{\textbf{C}}$ that 
are down-weighted. This regularization knob is tuned from $0$ modes (i.e. unweighted) to $21$ modes (i.e. full inverse 
covariance weighting). Over $\sim3$ orders of magnitude of signal loss results when using inverse covariance weighting. Also 
plotted for comparison are $2\sigma$ power spectrum upper limits for the unweighted case (dashed blue), inverse variance 
weighted case (red), and added-identity case (cyan). All three regularizations shown (black, red, cyan) perform similarly (when 
$\sim3$$-4$ modes are down-weighted for the black curve). Finally, a theoretical prediction for noise ($2\sigma$ error) is plotted 
as solid green.}
	\label{fig:sigloss_modeloop}
\end{figure*}

@@

\begin{equation}
\label{eq:sense}
p(k) = \frac{X^{2}Y \Omega_{eff} T_{sys}^{2}}{\sqrt{2N_{lsts}N_{seps}}\,t_{int}N_{days}N_{bls}N_{pols}}
\end{equation}

\begin{itemize}
\item $X^{2}Y$: Conversion factors from observing coordinates (angles on the sky) to cosmological coordinates (co-moving 
distances). For $z=8.4$, $X^{2}Y = 5 \times 10^{11} h^{-3} Mpc^{3} str^{-1} GHz^{-1}$.
\item $\Omega_{eff}$: The effective primary beam area in steradians (\citealt{parsons_et_al2010}; \citealt{pober_et_al2012}). 
The effective beam area changes with the application of a fringe-rate filter, since different parts of the beam are up-weighted and down-weighted. Using numbers from Table 1 in \citet{parsons_et_al2016}, $\Omega_{eff} = 0.74^{2}/0.24$ for an optimal fringe-rate 
filter. 
\item $T_{sys}$: The system temperature is set by:

@@

where $\nu$ are frequencies in GHz. We use a receiver temperature of $144$ K, yielding $T_{sys} = 431$ K at $150$ MHz. 
This is lower than the $T_{sys}$ of $500$ K used in A15 because of several small miscalculation errors that were 
identified\footnote{such as missing a square root in going from a variance to a standard deviation}.
\item $\sqrt{2}$: This factor in the denominator of the sensitivity equation comes from taking the real part of the power spectrum 
estimates after squaring visibility measurements. In A15, a factor of $2$ was mistakenly used.
\item $N_{lsts}$: The number of LST hours that go into a power spectrum estimation. The sensitivity scales as the square root 
because we integrate incoherently over time. For PAPER-64, $N_{lsts} = 8$ hours.
\item $N_{seps}$: The number of baseline separation types averaged incoherently in a final power spectrum estimate. For the 
analysis in this paper, we only use one type of baseline, hence $N_{seps}=1$. The updated limits in Kolopanis et al., \textit{in prep}
use three separation types.
\item $t_{int}$: The integration time of the data. It is crucial to adapt this number if filtering is applied along the time axis (i.e. a 
fringe-rate filter). We compute the effective integration time of our fringe-rate filtered data by scaling the original integration time $t_{i}$
using the following:
\begin{equation}
t_{int} = t_{i} \frac{\int1 \, df}{\int w^{2}(f) \,df},
\end{equation}
where $t_{i}=43$ seconds, $t_{int}$ is the fringe-rate filtered integration time, $w$ is the fringe-rate profile, and the integral is 
taken over all fringe-rates. For PAPER-64, this number is $t_{int} = 3857$ s. 
\item $N_{days}$: The total number of days of data analyzed. In A15, this number was set to $135$. However, because we 
divide our data in half (to form `even' and `odd' datasets), this number should be reduced by a factor of $2$. Additionally, 
because our LST coverage is not $100\%$ complete (it doesn't overlap for every single day), we compute a more realistic value of 
$N_{days}$ as:
\begin{equation}
 \frac{1}{N_{days}} = \sqrt{\Big\langle\frac{1}{N_{i}^{2}} \Big\rangle_{i}},
 \end{equation}
\noindent where $i$ is over LST (\citealt{jacobs_et_al2015}). For PAPER-64, our revised estimate of $N_{days}$ is $\sim34$ 
days.
\item $N_{bls}$: The number of baselines contributing to the sensitivity of a power spectrum estimate. In A15, this number was 
the total number of $30$ m East/West baselines used in the analysis. However, using the total number of baselines neglects 
the fact that baselines are averaged into groups (see Section \ref{sec:Boot}) before cross-multiplying data. Our revised estimate for the parameter is:
\begin{equation}
N_{bls} = \frac{N_{bls}}{N_{gps}}\sqrt{N_{gps}^{2}-N_{gps}},
\end{equation}
\noindent where, for the A15 analysis, $N_{gps} = 5$. Each baseline group averages down linearly as the number of baselines 
entering the group ($N_{bls}/N_{gps}$) and then as the square root of the number of cross-multiplied pairs ($\sqrt{N_{gps}^{2} - 
N_{gps}}$). For the revised PAPER-64 analysis with only one baseline separation type, this becomes $N_{bls} \sim 46$ instead 
of $51$. 
\item $N_{pols}$: The number of polarizations averaged together. For the case of Stokes I, $N_{pols}=2$.
\end{itemize}

@@

\begin{figure}
	\centering
	\includegraphics[width=\columnwidth]{plots/sense_check.png}
	\caption{An updated prediction for the noise-level of PAPER-64 data (black) is shown in comparison to previously 
published sensitivity limits (gray). Both sensitivity analyses plotted assume only one baseline type (an additional factor of $
\sqrt{3}$ for three baseline types is needed to match A15 exactly). Major factors that contribute to the discrepancy are $
\Omega_{eff}$, $N_{days}$ and $N_{bls}$, as described in Section \ref{sec:PSSense}, which when combined decreases our 
sensitivity (higher noise floor) by a factor of $\sim5$ in mK$^{2}$.}
	\label{fig:sense_check}
\end{figure}

To verify our thermal noise prediction, we form power spectra estimates using a pure noise simulation. We create Gaussian 
random noise assuming a constant $T_{sys}$ (neglecting sky variation) but accounting for the true $N_{days}$ as determined 
by LST sampling counts for each time and frequency in the LST-binned data. We convert $T_{sys}$ into a variance statistic 
using:

@@

We briefly discuss one way in which we mitigate foreground leakage in a power spectrum estimate, and two in which we 
suppress noise biases. These methods are not novel to this analysis but here we frame them in the context of minimizing false 
(non-EoR) detections.

@@

\noindent where $\textbf{R}$ is the data-weighting matrix and $\alpha$ and $\beta$ are wavebands in $k_{\parallel}$. We take 
the Cholesky decomposition of $\textbf{F}$, decomposing it into two lower triangular matrices:

@@

In addition to mitigating foreground bias at high $k$'s, two other sources of bias that we actively suppress in the PAPER-64 
analysis are noise bias associated with the squaring of thermal noise and noise bias from crosstalk. In order to avoid the 
former, we filter out certain cross-multiplications when forming $\widehat{q}$ in Equation \eqref{eq:qhat}. Namely, the PAPER-64 
dataset is divided into two halves: even julian dates and odd julian dates. Our data vectors are then $\textbf{x}_{even, 1}$ for 
the `even' dataset and baseline group $1$, $\textbf{x}_{odd, 1}$ for the `odd' dataset and baseline group $1$, etc. We only form 
$\widehat{q}$ when the two copies of $\textbf{x}$ come from different groups and baselines, never multiplying `even' with `even', for 
example, in order to prevent the squaring of the same thermal noise.

@@

\begin{figure}
	\centering
	\includegraphics[width=\columnwidth]{plots/null.png}
	\caption{Results for three null tests compared to the PAPER-64 revised power spectrum (black) and analytically estimated 
$2\sigma$ errors (gray shaded region). For each, we take a jackknife along a different axis of the dataset - along julian days (separating 
even and odd days; blue), along baselines (green), and along LST (magenta). We expect the sky signal to disappear for a `passing' null test. 
We find that the biases in our power spectrum are likely caused by variation of foregrounds in LST, and are not attributable to 
particular baselines or days of data.}
	\label{fig:null}
\end{figure}

Investigating Figure \ref{fig:null}, we find that both the baselines and even/odd null tests are consistent with noise. We note that 
the error bars for the baselines test (green) are especially small --- this is because the signal is effectively cancelled out prior to 
cross-multiplication (when forming baseline groups).

The null test in LST (magenta) is much more illuminating. The fact that there are many power spectrum points outside the 
estimated error region signifies that the bias we see is likely from foregrounds that vary in LST. In other words, $t_{1}$ and 
$t_{2}$ differ by an amount greater than thermal noise and they do not effectively cancel out the sky signal during cross-multiplication. The errors for this null test are also large, also reflective of residual foregrounds.

We do not investigate the detailed nature of the residual foregrounds in this paper, though one could imagine performing many 
similar null tests with a sliding window of $t_{1}$'s and $t_{2}$'s. This would illuminate the particular LST range that introduces 
the foreground bias (or whether the bias is constant in LST), and could potentially be traced to an individual bright radio source. 
This type of detailed analysis will be critical at EoR sensitivities, however, for our current analysis we are not surprised that the 
bias we see comes from foregrounds in regions where we expect leakage.

@@

\begin{itemize}
\item Signal loss, previously found to be $<2\%$ in A15, was under-estimated by a factor of $\sim$$1000$ for inverse 
covariance weighting. For our new analysis, we use a regularized covariance weighting method to minimize loss (Section 
\ref{sec:Weight}). However, because our revised weighting method is not as aggressive as the former, our results are still a 
factor of $\sim7$ mK higher than previous limits. Under-estimated signal loss therefore represents the bulk of our revision. We 
note that PAPER's analysis is not the first to under-estimate loss; results from the GMRT (\citealt{paciga_et_al2013}) were also 
revised from new signal loss calculations associated with their singular value decomposition foreground filter.
\item Power spectrum errors, originally computed by bootstrapping, were under-estimated by a factor of $\sim$$1.4$ in mK due to oversampling data whose effective number of independent samples was reduced from fringe-rate filtering (Section \ref{sec:Boot}). 
\item Several factors used in an analytic expression to predict the noise-level in PAPER-64 data were revised, yielding a 
decrease in predicted sensitivity level by a factor of $\sim$$2$ in mK (Section \ref{sec:PSSense}). We have verified our revised 
prediction extensively using pure noise simulations. We note that our sensitivity prediction is revised by a factor less than our 
power spectrum result, implying that if taken at face value, the theoretical prediction for noise in A15 was too high for its data 
points.
\end{itemize}

The $21$ cm future is exciting, as new experiments have sensitivities that expect to reach and surpass EoR levels, improved 
foreground mitigation/removal strategies are being developed, and simulations are being designed to better understand 
instruments. On the power spectrum analysis side, robust signal loss simulations, precise error calculations, and 
comprehensive jackknife tests will play critical roles in accurate $21$ cm results. With strong foundations being established now, it is safe to say that we can expect to learn much about reionization and our early Universe in the coming years.

@@

\section{Acknowledgements}
CC would like to acknowledge the UC Berkeley Chancellor's Fellowship, National Science Foundation Graduate Research 
Fellowship (Division of Graduate Education award 1106400), and thank Eric Switzer for helpful discussions. PAPER and HERA 
are supported by grants from the National Science Foundation (awards 1440343, and 1636646). ARP, DCJ, and JEA would 
also like to acknowledge NSF support (awards 1352519, 1401708, and 1455151, respectively). SAK is supported by the University of Pennsylvania School of Arts and Sciences Dissertation Completion Fellowship. We graciously thank SKA-SA for site infrastructure and observing support.
\label{sec:Ack}

@@

Formally we can express our test as: ``What is the $P_{\rm in}$ such that
\begin{equation}
\widehat{\textbf{p}}_{r} > \widehat{\textbf{p}}_{x} \Lambda,
\end{equation}  
where $\Lambda$ represents a choice of threshold?'' Of course, both sides of this equation are actually a distribution of values associated with data variance and injected model variance. One way to interpret this test for the two distributions is to compute the probability that the two distributions are not\footnote{i.e. the null test} the same.

>>>>

\begin{figure*}
	\centering
	\includegraphics[width=1\textwidth]{plots/sigloss_modeloop.png}
	\caption{Power spectra $2\sigma$ upper limits for $k=0.393$ h Mpc$^{-1}$ for fringe-rate filtered PAPER-64 data. Values 
are shown before (gray) and after (black) signal loss estimation as a function of number of eigenmodes of $\widehat{\textbf{C}}$ that 
are down-weighted. This regularization knob is tuned from $0$ modes (i.e. unweighted) to $21$ modes (i.e. full inverse 
covariance weighting). Over $\sim3$ orders of magnitude of signal loss results when using inverse covariance weighting. Also 
plotted for comparison are $2\sigma$ power spectrum upper limits for the unweighted case (dashed blue), inverse variance 
weighted case (red), and added-identity case (cyan); all are after signal loss estimation. All three regularizations shown (black, red, cyan) perform similarly (when 
$\sim3$$-4$ modes are down-weighted for the black curve). Finally, a theoretical prediction for noise ($2\sigma$ error) is plotted 
as solid green.}
	\label{fig:sigloss_modeloop}
\end{figure*}

@@

\begin{equation}
\label{eq:sense}
p(k) = \frac{X^{2}Y \Omega_{eff} T_{sys}^{2}}{\sqrt{2N_{lst}N_{seps}}\,t_{int}N_{days}N_{bls}N_{pols}}
\end{equation}

\begin{itemize}
\item $X^{2}Y$: Conversion factors from observing coordinates (angles on the sky and frequency) to cosmological coordinates (co-moving 
distances). For $z=8.4$, $X^{2}Y = 5 \times 10^{11} h^{-3} Mpc^{3} str^{-1} GHz^{-1}$.
\item $\Omega_{eff}$: The effective primary beam area in steradians (\citealt{parsons_et_al2010}; \citealt{pober_et_al2012}). 
The effective beam area changes with the application of a fringe-rate filter, since different parts of the beam are up-weighted and down-weighted. Using numbers from Table 1 in \citet{parsons_et_al2016}, $\Omega_{eff} = 0.74^{2}/0.24$ for an optimal fringe-rate 
filter. 
\item $T_{sys}$: The system temperature is set by:

@@

where $\nu$ are frequencies in GHz. We use a receiver temperature of $144$ K, yielding $T_{sys} = 431$ K at $150$ MHz. 
This is lower than the $T_{sys}$ of $500$ K used in A15 because of several small miscalculation errors that were 
identified\footnote{For example, there was a missing a square root in going from a variance to a standard deviation.}.
\item $\sqrt{2}$: This factor in the denominator of the sensitivity equation comes from taking the real part of the power spectrum 
estimates after squaring visibility measurements. In A15, a factor of $2$ was mistakenly used.
\item $N_{lst}$: The number of LST bins that go into a power spectrum estimation. The sensitivity scales as the square root 
because we integrate incoherently over time. For PAPER-64, $N_{lst} = 8$.
\item $N_{seps}$: The number of baseline separation types averaged incoherently in a final power spectrum estimate. For the 
analysis in this paper, we only use one type of baseline, hence $N_{seps}=1$. The updated limits in Kolopanis et al., \textit{in prep}
use three separation types.
\item $t_{int}$: Length of an independent integration of the data. It is crucial to adapt this number if filtering is applied along the time axis (i.e. a 
fringe-rate filter). We compute the effective integration time of our fringe-rate filtered data by scaling the original integration time $t_{i}$
using the following:
\begin{equation}
t_{int} = t_{i} \frac{\int1 \, df}{\int w^{2}(f) \,df},
\end{equation}
where $t_{i}=43$ seconds, $t_{int}$ is the fringe-rate filtered integration time, $w$ is the fringe-rate profile, and the integral is 
taken over all fringe-rates. For PAPER-64, this number is $t_{int} = 3857$ s. 
\item $N_{days}$: The total number of days of data analyzed. In A15, this number was set to $135$. However, because we 
divide our data in half (to form `even' and `odd' datasets), this number should be reduced by a factor of $2$. Additionally, 
because our LST coverage is not $100\%$ complete (it doesn't overlap for every single day), we compute a more realistic value of 
$N_{days}$ as:
\begin{equation}
 \frac{1}{N_{days}} = \sqrt{\Big\langle\frac{1}{N_{i}^{2}} \Big\rangle_{i}},
 \end{equation}
\noindent where $i$ is over LST (\citealt{jacobs_et_al2015}). For PAPER-64, our revised estimate of $N_{days}$ is $\sim34$ 
days.
\item $N_{bls}$: The number of baselines contributing to the sensitivity of a power spectrum estimate. In A15, this number was 
the total number of $30$ m East/West baselines used in the analysis. However, using the total number of baselines neglects 
the fact that baselines are averaged into groups (see Section \ref{sec:Boot}) for computational speed-up when cross-multiplying data. Our revised estimate for the parameter is:
\begin{equation}
N_{bls} = \frac{N_{bls}}{N_{gps}}\sqrt{N_{gps}^{2}-N_{gps}},
\end{equation}
\noindent where, for the A15 analysis, $N_{gps} = 5$. Each baseline group averages down linearly as the number of baselines 
entering the group ($N_{bls}/N_{gps}$) and then as the square root of the number of cross-multiplied pairs ($\sqrt{N_{gps}^{2} - 
N_{gps}}$). For the revised PAPER-64 analysis with only one baseline separation type, this becomes $N_{bls} \sim 46$ instead 
of $51$. 
\item $N_{pols}$: The number of polarizations averaged together. For the case of Stokes I, $N_{pols}=2$.
\end{itemize}

@@

\begin{figure}
	\centering
	\includegraphics[width=\columnwidth]{plots/sense_check.png}
	\caption{An updated prediction for the noise-level of PAPER-64 data (black) is shown in comparison to previously 
published sensitivity limits (gray). Both sensitivity analyses plotted assume only one baseline type (an additional factor of $
\sqrt{3}$ for three baseline types is needed to match A15 exactly). Major factors that contribute to the discrepancy are $
\Omega_{eff}$, $N_{days}$ and $N_{bls}$, as in Equation \eqref{eq:sense} and described in Section \ref{sec:PSSense}, which when combined decreases our 
sensitivity (higher noise floor) by a factor of $\sim5$ in mK$^{2}$.}
	\label{fig:sense_check}
\end{figure}

To verify our thermal noise prediction, we form power spectra estimates using a pure noise simulation. We create Gaussian 
random noise assuming a constant $T_{rcvr}$ (translated into $T_{sys}$ via Equation \eqref{eq:sys}) but accounting for the true $N_{days}$ as determined 
by LST sampling counts for each time and frequency in the LST-binned data. We convert $T_{sys}$ into a variance statistic 
using:

@@

We briefly discuss one way we mitigate foreground leakage in a power spectrum estimate, and two ways we 
suppress noise biases. These methods are not novel to this analysis but here we frame them in the context of minimizing false 
(non-EoR) detections.

@@

\noindent where $\textbf{R}$ is the data-weighting matrix and $\alpha$ and $\beta$ are wavebands in $k_{\parallel}$. We take 
the Cholesky decomposition of $\textbf{F}$, decomposing it into two lower triangular matrices (which is possible since $\textbf{F}$ is Hermitian):

@@

In addition to mitigating foreground bias at high $k$'s, two other sources of bias that we actively suppress in the PAPER-64 
analysis are noise bias associated with the squaring of thermal noise and noise bias from crosstalk. In order to avoid the 
former, we filter out certain cross-multiplications when forming $\widehat{q}$ in Equation \eqref{eq:qhat}. Namely, the PAPER-64 
dataset is divided into two halves: even julian dates and odd julian dates. Our data vectors are then $\textbf{x}_{even, 1}$ for 
the `even' dataset and baseline group $1$, $\textbf{x}_{odd, 1}$ for the `odd' dataset and baseline group $1$, etc. We only form 
$\widehat{q}$ when the two copies of $\textbf{x}$ come from different groups and baselines, never multiplying `even' with `even', for 
example, in order to prevent the squaring of the same thermal noise. We recognize that this method results in a hit to our sensitivity. Sensitivity can be gained, for example, by only dividing up the dataset once (either along time or baselines), or by creating more groups (more cross-multiplications), but in this paper we only attempt to revise the A15 analysis (which uses the same groupings), not produce the most sensitive limits of PAPER-64.

@@

\begin{figure*}
	\centering
	\includegraphics[width=1\textwidth]{plots/null.png}
	\caption{Results for three null tests compared to the PAPER-64 revised power spectrum (black) and analytically estimated 
$2\sigma$ errors (gray shaded region). For each, we take a jackknife along a different axis of the dataset - along julian days (separating 
even and odd days; blue), along baselines (green), and along LST (magenta). We expect the sky signal to disappear for a `passing' null test (for all error bars to be contained to within the gray shaded region).
We find that none of the null tests performed pass, and that the dominant source of the biases in our power spectrum are likely caused by variation of foregrounds in LST (due to the magenta result being the most inconsistent with noise)}
	\label{fig:null}
\end{figure*}

Investigating Figure \ref{fig:null}, we find that none of the null tests are fully consistent with noise; we would expect the null tests' error bars to be contained within the gray shaded region (theoretical error) for a `passable' test. We note, however, that the error bars for the baselines test (green) and even/odd test (blue) are smaller than those of the LST test (magenta).

%We note that the error bars for the baselines test (green) are especially small --- this is because the signal is effectively cancelled out prior to cross-multiplication (when forming baseline groups).

This suggests that the primary systematic driving our power spectrum points and errors to be outside the 
estimated error region is LST-dependent, and therefore likely to be residual foregrounds. In other words, $t_{1}$ and 
$t_{2}$ differ by an amount greater than thermal noise and they do not effectively cancel out the sky signal during cross-multiplication. While residual foregrounds are the primary cause for power spectrum results above the theoretical noise (as in Figure \ref{fig:ps1_data}), other unexplained variations exist which are present in all the null tests. These variations could be attributable to... \cc{fill in}

We do not investigate the detailed nature of the residual foregrounds in this paper, though one could imagine performing many 
similar null tests with a sliding window of $t_{1}$'s and $t_{2}$'s. This would illuminate the particular LST range that introduces 
the foreground bias (or whether the bias is constant in LST), and could potentially be traced to an individual bright radio source. 
This type of detailed analysis will be critical at EoR sensitivities, however, for our current analysis we are not surprised that the main source of
bias we see comes from foregrounds in regions where we expect leakage.

@@

\begin{itemize}
\item Signal loss, previously found to be $<2\%$ in A15, was under-estimated by a factor of $\sim$$1000$ for inverse 
covariance weighting. For our new analysis, we use a regularized covariance weighting method to minimize loss (Section 
\ref{sec:Weight}). However, because our revised weighting method is not as aggressive as the former, our results are still a 
factor of $\sim7$ in mK higher than previous limits. Under-estimated signal loss therefore represents the bulk of our revision. We 
note that PAPER's analysis is not the first to under-estimate loss; results from the GMRT (\citealt{paciga_et_al2013}) were also 
revised from new signal loss calculations associated with their singular value decomposition foreground filter.
\item Power spectrum errors, originally computed by bootstrapping, were under-estimated by a factor of $\sim$$1.4$ in mK due to oversampling data whose effective number of independent samples was reduced from fringe-rate filtering (Section \ref{sec:Boot}). 
\item Several factors used in an analytic expression to predict the noise-level in PAPER-64 data were revised, yielding a 
decrease in predicted sensitivity level by a factor of $\sim$$2$ in mK (Section \ref{sec:PSSense}). We have verified our revised 
prediction extensively using pure noise simulations. We note that our sensitivity prediction is revised by a factor less than our 
power spectrum result, implying that if taken at face value, the theoretical prediction for noise in A15 was too high for its data 
points.
\end{itemize}

The future of $21$ cm cosmology is exciting, as new experiments have sensitivities that expect to reach and surpass EoR levels, improved 
foreground mitigation/removal strategies are being developed, and simulations are being designed to better understand 
instruments. On the power spectrum analysis side, robust signal loss simulations, precise error calculations, and 
comprehensive jackknife tests will play critical roles in accurate $21$ cm results. With strong foundations being established now, it is safe to say that we can expect to learn much about reionization and our early Universe in the coming years.

@@

\section{Acknowledgements}
CC would like to acknowledge the UC Berkeley Chancellor's Fellowship, National Science Foundation Graduate Research 
Fellowship (Division of Graduate Education award 1106400), and thank Eric Switzer for helpful discussions. PAPER and HERA 
are supported by grants from the National Science Foundation (awards 1440343, and 1636646). ARP, DCJ, and JEA would 
also like to acknowledge NSF support (awards 1352519, 1401708, and 1455151, respectively). SAK is supported by the University of Pennsylvania School of Arts and Sciences Dissertation Completion Fellowship. JSD acknowledges NSF AAPF
award 1701536. We graciously thank SKA-SA for site infrastructure and observing support.
\label{sec:Ack}

@@

Formally we can express our test as: ``What is the $P_{\rm in}$ such that
\begin{equation}
\widehat{\textbf{p}}_{r} > \widehat{\textbf{p}}_{x} \Lambda,
\end{equation}  
where $\Lambda$ represents a choice of threshold?'' Of course, both sides of this equation are actually a distribution of values associated with data variance and injected model variance. One way to interpret this test for the two distributions is to compute the probability that the two distributions are not (i.e. the null test) the same.
